NFL Draft Analysis

### 2020-05-12 draft_analysis.Rmd
Fix working directory

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(tidyverse)
library(rvest)
library(gridExtra)
library(caret)
library(knitr)
setwd("/Users/PhilipIpe/Documents/Data Science/Projects/NFL Draft Analytics/")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
library(tidyverse)
library(rvest)
library(gridExtra)
library(caret)
library(knitr)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```
